### 2017-09-04 paper/evaluation.tex
Using macro
Removed outdated comments
Added some new lines

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.
Overall, we found, using this methodology, \numProjectsParStatic{}
projects that use parallelism.
Compared to the set of projects listed in
Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration C3), \CodeIn{Mapstruct} (using configuration
\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
and \CodeIn{Takes} were not detected using this methodology.
That happened because these projects loaded a \emph{pom.xml} file from
a jar file that we did not check.  Considering the static and dynamic
methods together, we found a total of \numProjectsParTotal{} distinct
projects using parallelism, corresponding to the union of the two
subject sets.

@@

%False positive can happen because of comments, for instance.  
%To eliminate the cases of false positives and also to categorize 
%true positive cases, we complemented the initial mining step with a 
%manual inspection of files.
%% settings); the second step (inspection) consists in a manual
%% inspection to confirm the presence of parallelism settings in the
%% build file and classify them according to the parallelism level.
%% Figure \Fix{removed} describes the discovery step: we list the paths
%% of all build files and filter only the files that contain any of the

%% Figure~\ref{tab:inspection-table} summarizes our results.
%% \Fix{The first column indicates the group of projects according to
%% their time cost.  The second column indicates the number of build
%% files per group.  The last column indicates the ratio of projects with
%% parallelization settings.  From the \numMedLong{} subjects, we found
%% \pomMedLong{} \pomf{} files.  The \numPomMatched{} configurations are
%% distributed across \numProjectsPar{} projects from our sample.}

%% % \emph{From these results we found that $\sim$51\% of medium and
%% % long-running projects do not use parallel features to run test
%% % suites.}\Mar{please make it consistent with research
%% % question}\Mar{explain this is over(under)-estimated...}
%% \begin{figure}[ht!]
%%     \centering
%%     \resizebox{.48\textwidth}{!}{%
%%     \begin{tabular}{llcl}
%%         \toprule
%%         Group & Subject & \# of modules & Mode\\%
%%         \midrule%
%%         Long   &JenkinsCI Gerrit Trigger Plugin& 1 & \ForkSeq\\%
%%         Medium &Bouncestorage Chaos Http Proxy & 1 & C2\\%
%%         Medium &Javaslang & 1 & C3\\%
%%         Medium &Apache Flink & 1 &\ForkSeq\\%
%%         Medium &Apache Logging Log4J2 & 3 & \ForkSeq{}\\%
%%         Medium &Google Cloud Platform DataflowJavaSDK & 1 & C3\\%
%%         Medium &Hazelcast Jet & 1 & \ForkSeq\\%
%%         Medium &Jankotek MapDB & 1 & C3\\%
%%         Medium &Mapstruct & 1 & \ForkSeq\\%
%%         Medium &Spotify Helios & 3 & \ForkSeq\\%
%%         \bottomrule%
%%     \end{tabular}}
%%     \caption{Subjects with parallelization configurations in build files.}
%%     \label{tab:inspection-table}
%% \end{figure}

%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{results/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

@@

\begin{table}[h!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & 
    \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Jenkins CI }Gerrit\Comment{ Plugin} & 51.19m & 40.31m &  1.26x\\%
Medium &\Comment{ Spotify }Helios& 4.46m & 1.63m & 2.73x\\%  
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m &
    \cellcolor{lightgray}9.2x\\%
Medium &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
  execution ($T_p$) over sequential execution ($T_s$).  Default
  parallel configuration of Maven is used.  Highest slowdown/speedup
  appears in gray color.}
\end{table}

>>>>

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.
Overall, we found, using this methodology, \numProjectsParStatic{}
projects that use parallelism.
Compared to the set of projects listed in
Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
and \CodeIn{Takes} were not detected using this methodology.
That happened because these projects loaded a \emph{pom.xml} file from
a jar file that we did not check.  Considering the static and dynamic
methods together, we found a total of \numProjectsParTotal{} distinct
projects using parallelism, corresponding to the union of the two
subject sets.

@@

@@

\begin{table}[h!]
\centering
\resizebox{.41\textwidth}{!}{%
  \scriptsize
\begin{tabular}{llrrr}
\toprule
\emph{Group} & \emph{Subject} & \multicolumn{1}{c}{$T_s$} & \multicolumn{1}{c}{$T_p$} & $T_s/T_p$ \\%
\midrule%
Medium & Californium & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
Medium & \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1.51m & 1.47m & \cellcolor{lightgray}1.01x\\%
Medium &\Comment{ Apache }Flink& 11.79m & 2.57m & 4.59x\\%
Long &\Comment{ Apache }Log4J2& 8.24m & 8.21m & \cellcolor{lightgray}1.00x\\%
Medium &Javaslang& 2.18m & 1.82m & 1.19x\\%
Medium &Jcabi\Comment{ GitHub} & 2.76m & 0.30m & \cellcolor{lightgray}9.2x\\%
Long &\Comment{ Hazelcast }Jet& 8.26m & 3.67m & 2.25x\\%
Long & \Comment{apache} Mahout & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
Long &\Comment{ Jankotek }MapDB& 10.06m & 8.58m & 1.17x\\%
Medium & \Comment{apache} OpenNLP & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
Medium & \Comment{yegor256} Rultor & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
Medium & \Comment{yegor256} Takes & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
Long & \Comment{vavr-io} Vavr & \Fix{Xm} & \Fix{Xm} & \Fix{Yx}\\%
\midrule
\textbf{average} &  &  &  & \avgSpeedup{}x\\
\bottomrule%
\end{tabular}}
\caption{\label{tab:speedup}Speedup (or slowdown) of parallel
  execution ($T_p$) over sequential execution ($T_s$).  Default
  parallel configuration of Maven is used.  Highest slowdown/speedup
  appears in gray color.}
\end{table}
